Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex

	Reduction \fbox{$ \judgeCreduce{s}{s} $}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}

	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{(\kOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}

@@

If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
and be confident that this cast representation is valid.

Some cast representations are also \textit{monoids}. This definition is useful 
in the proof of our framework, and might be interesting for other people.

\begin{definition}[Monoid]
	A Cast ADT is a monoid if 
	for all
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c_1) = c_1$,
		\item $seq(c_1,id(T_2)) = c_1$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics indexed by Cast ADT ($ C $). When $ C $ is a Lazy 
D Cast ADT, \effCEK{C} repects \ineffCEKD.
In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
and only if $ \judgeSeval{C}{e}{o} $. In 
subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
a Lazy D Cast ADT, \evalEqv{\ineffCEKD}{\effCEK{C}}.

>>>>

	Reduction \fbox{$ \judgeCreduce{s}{s} $}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{(\kOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{(\kOOinl{\kappa})}
	}{}
	\redrule{
	\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{(\kOOinr{\kappa})}
	}{}
	\redrule{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{(\kOOappI{E}{e_2}{\kappa})}}{}

@@

After showing their cast representation is a Lazy D Cast, users of our 
frameworks can plug-in this cast representation to our space-efficient abstract 
machine in subsection~\ref{ssec:framework:cek}, and prove that this machine is 
equivalent to \ineffCEKD\ (subsection~\ref{secc:framework:all-correct}), which 
depends on lemmas in subsection~\ref{secc:framework:monoid-correct}.
